---
title: "danish-fire"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{danish-fire}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tevt)
```

Adding the data to the current workspace
```{r get-data}
data(danish)
```

## Hill Plots

The standard averaged hill plot
```{r}
gpd.plot.hill1(danish) 
```
Alternative Hill plot over the interval $[0,1]$ with confidence intervals
```{r}
gpd.plot.hill2(danish, conf.int = TRUE) 
```
QQ-Estimator Plot
```{r}
gpd.qq.est(danish)
```



## Double Bootstrap for OSF (Optimal Sample Fraction)
An Implementation of the procedure proposed in Gomes et al. (2012) and Caeiro et al. (2016) for selecting the optimal sample fraction in tail index estimation.
```{r gomes}
gomes = gpd.gomes(danish)
out = gpd.fit(danish, threshold=gomes$threshold)
gpd.diag(out, safe=TRUE)
```

## Double Bootstrap for OSF (Optimal Sample Fraction)
n Implementation of the procedure proposed in Danielsson et al. (2001) for selecting the optimal sample fraction in tail index estimation.
```{r danielsson}
danielsson = gpd.danielsson(danish)
out = gpd.fit(danish, threshold=danielsson$threshold)
gpd.diag(out, safe=TRUE)
```

## Single Bootstrap for OSF (Optimal Sample Fraction)
An Implementation of the procedure proposed in Hall (1990) for selecting the optimal sample fraction in tail index estimation
```{r hall}
hall = gpd.hall(danish)
out = gpd.fit(danish, threshold=hall$threshold)
gpd.diag(out, safe=TRUE)
```

## Automated Approach for Hill-Plot
An Implementation of the so called Eye-balling Technique proposed in Danielsson et al. (2016)
```{r eye}
eye = gpd.eye(danish)
out = gpd.fit(danish, threshold=eye$threshold)
gpd.diag(out, safe=TRUE)
```

## Fitting the Minimum Distance model
Minimising the distance between the empirical tail and a theoretical Pareto tail with respect to k. An Implementation of the procedure proposed in Danielsson et al. (2016) for selecting the optimal threshold in extreme value analysis.
```{r md}
md = gpd.md(danish)
out = gpd.fit(danish, threshold=md$threshold)
gpd.diag(out, safe=TRUE)
```

## Old Vignette stuff
Fitting the model
```{r}
out <- gpd.fit(danish, threshold=25)
```

Cheap and easy diagnostic plots 
At some point, this needs to override S3 plot function
```{r}
gpd.plot(out, pick=1)
gpd.plot(out, pick=2)
gpd.plot(out, pick=3)
#gpd.plot(out, pick=4)
```
Better diagnostic plots, differs whether model is stationary.
```{r}
gpd.diag(out, safe=TRUE)
```
But each of these can be accessed independently using their associated function names
```{r}
gpd.qq2(out)
```

```{r}
gpd.hist(out)
```

```{r}
gpd.rlPlot(out)
```


